### 2014-03-20 manuscript.tex
Described parsing, added new section in 3

The parser used in this study is trained on the Norwegian Dependency Treebank (NDT). The NDT is a corpus built up at the National Library of Norway in the period 2011-2013, manually annotated with part-of-speech tags, morphological features, syntactic functions and dependency graphs \cite{Sol14, Sol13}. It consists of approximately 600 000 tokens, equally distributed between Norwegian Bokmål and Nynorsk, the two Norwegian written standards. Only the Bokmål subcorpus has been used here. A large proportion of the NDT is newspaper text, there are also parliament transcripts, government reports and texts with a more colloquial style from blogs. Detailed annotation guidelines in English will be made available in April 2014 \cite{Kinn2013}.

@@

>>>>

\paragraph{Dependency distance}
One way of expressing the syntactic environment of a target word with respect to a sentiment word is to determine its distance in the dependency graph. We define a distance function $\mathbf{depdist}(kw_i, sw_{j})$ which returns the number of nodes between the two words in the parse tree plus one.

@@

\subsection{Corpus postprocessing}
The sentiment corpus was PoS-tagged and parsed using the
Bohnet\&Nivre-parser \cite{Boh:Niv:12}. This parser is a
transition-based dependency parser with joint tagger that implements
global learning and a beam search for non-projective labeled
dependency parsing.  This latter parser has recently outperformed
pipeline systems (such as the Malt and MST parsers) both in terms of
tagging and parsing accuracy for typologically diverse languages such
as Chinese, English, and German. It has been reported to obtain a
labeled accuracy of 87.7 for Norwegian \cite{Sol14}.  The parser is
trained on the Norwegian Dependency Treebank (NDT). The NDT is a
treebank created at the National Library of Norway in the period
2011-2013, manually annotated with part-of-speech tags, morphological
features, syntactic functions and dependency graphs \cite{Sol14,
  Sol13}. It consists of approximately 600 000 tokens, equally
distributed between Norwegian Bokm{\aa}l and Nynorsk, the two Norwegian
written standards. Only the Bokm{\aa}l subcorpus has been used here. A
large proportion of the NDT is newspaper text, there are also
parliament transcripts, government reports and texts with a more
colloquial style from blogs. Detailed annotation guidelines in English
will be made available in April 2014 \cite{Kinn2013}.
